---
title: "Rx Label Syntax Documentation"
# title: "mrgsolve::ev_rx()"
# title: "&nbsp;"
output:
  html_document:
    number_sections: false
    fig_width: 7
    fig_height: 6
    fig_caption: true
    theme: yeti
    highlight: pygments

---

<head>
<link rel="stylesheet" type="text/css" href="style.css">
</head>

# Create intervention objects from Rx input


Source: `https://mrgsolve.org/docs/reference/ev_rx.html`


See details below for Rx specification. Actual parsing is done by
parse_rx; this function can be used to debug Rx inputs.


```{r, eval=FALSE}
mrgsolve::ev_rx(x, y, ...)

# S4 method for mrgmod,character
mrgsolve::ev_rx(x, y, ...)

# S4 method for character,missing
mrgsolve::ev_rx(x, df = FALSE, ...)

mrgsolve::parse_rx(x)
```
<!-- ::: -->
<!-- ::: -->

<!-- ::: {#arguments} -->
## Arguments


<dl>
  <dt><strong>x</strong></dt>
  <dd>&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; a model object or `character` Rx input</dd>
  <dt><strong>y</strong></dt>
  <dd>&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; `character` Rx input; see details</dd>
  <dt><strong>...</strong></dt>
  <dd>&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; not used at this time</dd>
  <dt><strong>df</strong></dt>
  <dd>&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; if `TRUE` then a data frame is returned</dd>
</dl>




<!-- x <br> -->
<!-- : &nbsp;&nbsp;&nbsp;&nbsp; a model object or `character` Rx input -->

<!-- y -->
<!-- : \ \ \ \ \ \ `character` Rx input; see details -->

<!-- \... -->
<!-- : \ \ \ \ \ \ not used at this time -->

<!-- df -->
<!-- : \ \ \ \ \ \ if `TRUE` then a data frame is returned -->





## Value

The method dispatched on model object (`mrgmod`) returns another model
object. The `character` method returns an event object. The `parse_rx`
function return a list named with arguments for the event object
constructor `ev`.



## Rx specification

-   The dose is found at the start of the string by sequential digits;
    this may be integer, decimal, or in scientific notation

-   Use `in` to identify the dosing compartment number; must be integer

-   Use `q` to identify the dosing interval; must be integer or decimal
    number (but not scientific notation)

-   Use `over` to indicate an infusion and its duration; integer or
    decimal number

-   Use `x` to indicate total number of doses; must be integer

-   Use `then` or `,` to separate dosing periods

-   User `after` to insert a lag in the start of a period; integer or
    decimal number (but not scientific notation)



## Examples

``` {r, eval=FALSE}
# example("ev_rx")

mrgsolve::ev_rx("100")
#> Events:
#>   time amt cmt evid
#> 1    0 100   1    1

mrgsolve::ev_rx("100 in 2")
#> Events:
#>   time amt cmt evid
#> 1    0 100   2    1

mrgsolve::ev_rx("100 q12 x 3")
#> Events:
#>   time amt ii addl cmt evid
#> 1    0 100 12    2   1    1

mrgsolve::ev_rx("100 over 2")
#> Events:
#>   time amt rate cmt evid
#> 1    0 100   50   1    1

mrgsolve::ev_rx("100 q 24 x 3 then 50 q12 x 2")
#> Events:
#>   time amt ii addl cmt evid
#> 1    0 100 24    2   1    1
#> 2   72  50 12    1   1    1

mrgsolve::ev_rx("100 then 50 q 24 after 12")
#> Events:
#>   time amt ii addl cmt evid
#> 1    0 100  0    0   1    1
#> 2   12  50 24    0   1    1

mrgsolve::ev_rx("100.2E-2 q4")
#> Events:
#>   time   amt ii cmt evid
#> 1    0 1.002  4   1    1

mrgsolve::ev_rx("100 over 2.23")
#> Events:
#>   time amt     rate cmt evid
#> 1    0 100 44.84305   1    1

mrgsolve::ev_rx("100 q 12 x 3")
#> Events:
#>   time amt ii addl cmt evid
#> 1    0 100 12    2   1    1

mrgsolve::parse_rx("100 mg q 24 then 200 mg q12")
#> [[1]]
#> [[1]]$time
#> [1] 0
#> 
#> [[1]]$cmt
#> [1] 1
#> 
#> [[1]]$amt
#> [1] 100
#> 
#> [[1]]$ii
#> [1] 24
#> 
#> 
#> [[2]]
#> [[2]]$time
#> [1] 0
#> 
#> [[2]]$cmt
#> [1] 1
#> 
#> [[2]]$amt
#> [1] 200
#> 
#> [[2]]$ii
#> [1] 12
#> 
#> 
```


Developed by Kyle T Baron.



Site built with `pkgdown`
2.0.1.

